No Replication Without Process Documentation:  An Assessment of Management

### 2020-03-26 R/MSE manuscript.Rmd
Add use of here() package; correct number of climate change MSEs

```{r load data, include=FALSE}
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

load("MSEreview.RData")

@@

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019. This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE, removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. Of the 264 articles, 11 included climate change as a driver of fishery status, and after removing other articles 154 articles document a MSE.

| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 11 |  
*Estimated by extrapolating from the assessed MSEs to the full set for now, the submission will contain an final count.

>>>>

```{r load data, include=FALSE}
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables
library(here) # file directory assistance

load(here("data/MSEreview.RData"))

@@

# Methods 
## Finding and Sampling the MSE Literature 
We conducted our search for MSEs in the SCI-EXPANDED index from Web of Science, searching for “management strategy evaluation” by topic across all years on January 8th, 2019. This search returned 264 results.  We reviewed a random sample of 30 articles that document a MSE, removing articles that were reviews, meta-analyses, or simply cited other MSE articles from our sample. After removing other articles from the original set of 264 articles, 154 articles document a MSE and 13 of these included climate change as a driver of fishery status. To give as full a picture of the climate change MSE to date as possible we have also reviewed the additional climate change MSE

| MSE type | Count |
|:--:|:--:|
| Published | 154 |
| Random Sample | 30 |
| Climate Change | 13 |  
*Estimated by extrapolating from the assessed MSEs to the full set for now, the submission will contain an final count.
